State of the Practice for Lattice Boltzmann Method Software

### 2022-01-22 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
Rearrangement of Section 2 of LBM SOP paper

We developed a methodology for evaluating the state of the practice of
scientific software \citep{SmithEtAl2021}.  The methodology aims to answer the
research questions posed in the previous section. This methodology can be
instantiated for a specific domain of scientific software, which in the current
case is LBM software.  The first section below describes the steps of the
process we used to select, measure and compare LBM software. This is followed by
quality definitions and how these qualities were assessed in our project. The
rest of the section provides the details of the methodology.
% an overview of the specifics of candidate software selection, the quantitative
% measurements, developer interviews, the ranking process via AHP and
% interaction with the Domain Expert.

\subsection{Overall Process}

\begin{enumerate}
	\item List candidate software packages for the domain. This is discussed in
	Section~\ref{identifysoftware}.
	\item Filter the software package list. This is discussed in
	Section~\ref{filtersoftware}.
	\item Gather the source code and documentation for each software package.
	\item Collect quantitative measures from the project repositories. This is
	discussed in Section~\ref{empiricalmeasures}.
	\item Measure using the measurement template. This is discussed in
	Section~\ref{empiricalmeasures}. The full measurement template can be found
	in \citet{SmithEtAl2021}.
	\item Survey the developers. The developers of each software package in the
	filtered software list were contacted for voluntary interviews. The details
	are given in Section~\ref{SecSurvey}.
	\item Use AHP to rank the software packages. This is discussed in
	Section~\ref{AHP}.
	\item Analyze the results and answer the research questions. The answers can
	be found in Section~\ref{answersquestions}.
\end{enumerate}

@@

@@

Part of how we address \rqref{RQ_CompareToolsProjMngmnt},
\rqref{RQ_CompareMethodologies}, \rqref{RQ_PainPoints} (which enables
\rqref{RQ_ComparePainPoints}, and \rqref{RQ_Concerns} (which enables
\rqref{RQ_CompareConcerns}). We designed a list of 20 questions to guide our
interviews, which can be found in \citet{SmithEtAl2021}. Some questions are
about the background of the software, the development teams, the interviewees,
and how they organize the projects. We also ask about the developer's
understandings of the users. Some questions focus on the current and past
difficulties, and the solutions the team has found, or will try. We also discuss
the importance and current situations of documentation. A few questions are
about specific software qualities, such as maintainability, understandability,
usability, and reproducibility. The interviews are semi-structured based on the
question list; we ask follow-up questions when necessary. Based on our
experience, the interviewees usually bring up some exciting ideas that we did
not expect, and it is worth expanding on these topics.

>>>>

We developed a methodology for evaluating the state of the practice of
scientific software \citep{SmithEtAl2021}. This methodology can be instantiated
for a specific domain of scientific software, which in the current case is LBM
software.  Since we group best practices around conventional software qualities,
the first section below provides definitions for the qualities of interest
(Section~\ref{softwarequalities}), along with information on how we assessed
these qualities. The following section (Section~\ref{Sec_OverallProcess})
provides an overview of the steps we used to select, measure and compare LBM
software.  The remaining sections provide details on each step of the steps in
the methodology. 
% of the next sections provide an overview of the specifics of identifying
% (Section~\ref{identifysoftware}) and filtering (Section~\ref{filtersoftware})
% the candidate software, our quantitative measurements
% (Section~\ref{empiricalmeasures}), the AHP ranking process
% (Section~\ref{AHP}), developer interviews (Section~\ref{SecSurvey}), and
% interactions with one of the key members of the assessment team -- the Domain
% Expert (Section~\ref{sec_vet_software_list}).

@@

\subsection{Overall Process} \label{Sec_OverallProcess}

\begin{enumerate}
	\item List candidate software packages for the domain.
	(Section~\ref{identifysoftware})
	\item Filter the software package list. (Section~\ref{filtersoftware})
	\item Gather the source code and documentation for each software package.
	\item Collect quantitative measures from the project repositories.
	(Section~\ref{empiricalmeasures})
	\item Measure using the measurement template.  The full measurement template
	can be found in \citet{SmithEtAl2021}. (Section~\ref{empiricalmeasures})
	\item Survey the developers. (Section~\ref{SecSurvey})
	\item Use AHP to rank the software packages. (Section~\ref{AHP})
	\item Analyze the results and answer the research questions.
\end{enumerate}

@@

Part of how we address \rqref{RQ_CompareToolsProjMngmnt},
\rqref{RQ_CompareMethodologies}, \rqref{RQ_PainPoints} (which enables
\rqref{RQ_ComparePainPoints}, and \rqref{RQ_Concerns} (which enables
\rqref{RQ_Recommend}). We designed a list of 20 questions to guide our
interviews, which can be found in \citet{SmithEtAl2021}. Some questions are
about the background of the software, the development teams, the interviewees,
and how they organize the projects. We also ask about the developer's
understandings of the users. Some questions focus on the current and past
difficulties, and the solutions the team has found, or will try. We also discuss
the importance and current situations of documentation. A few questions are
about specific software qualities, such as maintainability, understandability,
usability, and reproducibility. The interviews are semi-structured based on the
question list; we ask follow-up questions when necessary. Based on our
experience, the interviewees usually bring up some exciting ideas that we did
not expect, and it is worth expanding on these topics.
